Effect of resonant and random excitation on the LHC beam in the context of pulsed hollow electron lens operation.

### 2018-02-14 resex.tex
comments from Giulio including 8th turn pulsing

\section{Experimental and simulation setup\label{sec:exp}}
%put picture on top
\begin{figure*}
	\begin{minipage}[t]{1.0\linewidth}
		\centering
		2016 experiment\\
		\includegraphics[width=0.9\linewidth]{bunchfilling_2016.png}	
	\end{minipage}
	\begin{minipage}[t]{1.0\linewidth}
		\centering
		$ $\\
		2017 experiment\\
		\includegraphics[width=0.9\linewidth]{bunchfilling_2017.png}	
	\end{minipage}
	\caption{\label{fig:fill} Filling and excitation scheme for LHC experiments in 2016 (top) and 2017 (bottom). In 2016 the same excitation amplitude was applied on a group of 4 bunch while in 2016 the number was increased to 6 bunches. In 2016 the excitation was also only applied in one plane leading to $2\times24=48$ bunches in total in 2016 and $3\times2\times36=216$ bunches in 2017.}
\end{figure*}
%put picture on top

@@

The ADT kicker deflection angle is calculated from the kicker geometry and the excitation voltage on the deflection plates. The excitation voltage used in the experiments is a complicated waveform, generated by a very complex hardware (digital signal processor, chain of transmission lines, low and high power amplifiers). The peak excitation voltage (and subsequently the kick) seen by the beam can be only indirectly measured using the probes on each kicker. The measured values are therefore believed to be known with an error margin of 10-15\% for the experiments in 2017 and 50\% in 2016. The error in 2016 is much larger as no calibration of the ADT was performed beforehand, which was done in 2017. The maximum kick strength reachable with the ADT at injection without risking saturation is 96~nrad. As an example Fig.~\ref{fig:fill_meas} shows the oscillation amplitude of each bunch in both H and V planes captured by the LHC real time transverse activity monitor during the 2017 experiments and an excitation with $8^{\mathrm{th}}$ turn pulsing. The measured activity is well in line with the expected excitation pattern.
\begin{figure}[h]
	\centering
	\includegraphics[width=1.0\linewidth]{bunchfilling_measured.png}	
	\caption{\label{fig:fill_meas} Bunch by bunch excitation detected by the real time transverse activity monitor during the 2017 experiment and an excitation with 8th turn pulsing.}
\end{figure}

@@

The losses measured during the experiment however differ from the simulations in terms of for which case the largest rate is observed as well as quantitatively for the specific cases. For example smaller losses are expected for the 2016 experiments compared to the 2017 experiments from simulations, while experimentally higher loss rates were measured in 2016 (see Fig.~\ref{fig:7thexploss}). For the 2017 experiment, the highest loss rates are expected for pulsing in H+V, than in H and then with a considerably reduction in V. During the experiment comparable loss rates are however measured for all three planes (see Appendix~\ref{app:sec:7}, Fig.~\ref{fig:7thexploss2017}). Last but not least the loss rates as defined in Eqn.~\ref{eqn:lossrate} for the 2016 (red and yellow) and 2017 (black and gree) experiments are compared in Fig.~\ref{fig:7thexploss}. In both cases and as also observed for the $10^{\mathrm{th}}$~turn pulsing, the loss rate follows a quadratic scaling with the excitation amplitude. Loss rates were in general higher during the 2016 experiments. The loss rates from simulations are not shown in Fig.~\ref{fig:7thexploss} as losses were only observed for much higher excitation amplitudes than tried in the experiments.
	\includegraphics[width=1.0\linewidth]{2016+2017_scale_amp_7h_lblshort.png}
	\caption{\label{fig:7thexploss} Comparison of scaling of loss rates with excitation amplitude for $7^{\mathrm{th}}$~turn pulsing in H and data obtained during the 2016 experiment (black and blue) and 2017 experiment (red and yellow). The excitation amplitude error is 50\% in 2016 and was reduced to 15\% in 2017. The solid and dashed line indicate the second order polynomial fit to the loss rate.}

@@

\subsection{$8^{\mathrm{th}}$ turn pulsing\label{sec:simex8}}
Pulsing patterns which have little effect on the beam core are particularly interesting for the hollow electron lens operation if they in addition have a large effect on the halo, which is in general feasible considering the highly nonlinear field generated at the location of the halo particles by the HEL. With this motivation in mind the $8^{\mathrm{th}}$~turn pulsing pattern was studied, for which a small effect in comparison to the $7^{\mathrm{th}}$ and $10^{\mathrm{th}}$ turn pulsing is expected from the distribution tracking summarized in Fig.~\ref{fig:8thsim}.
		\includegraphics[width=1.0\linewidth]{2017injerra2b2uran1_2e-3_8th_3_5um_intensity.png}
		\includegraphics[width=1.0\linewidth]{2017injerra2b2uran1_2e-3_8th_3_5um_sigm.png}
		\includegraphics[width=1.0\linewidth]{2017injerra2b2uran1_2e-3_8th_3_5um_emit1.png}
		\includegraphics[width=1.0\linewidth]{2017injerra2b2uran1_2e-3_8th_3_5um_emit2.png}
	\caption{\label{fig:8thsim} Relative intensity (top left), bunch length (top right), and horizontal (bottom left) and vertical (bottom right) emittance obtained from simulations (distribution tracking) based on the 2017 injection optics with standard errors and $(Q_x,Q_y)=(62.27,60.295)$. The solid line indicates an excitation with only a random dipole noise component in H+V of 6~nrad, and the dotted and dashed line the results for $8^{\mathrm{th}}$~turn pulsing plus a random dipole noise component in H+V of 6~nrad.}
%\end{figure}
%\begin{figure}[t]
		no excitation
		\includegraphics[width=1.0\linewidth]{2017injnocolc15o+19_6noerru_dp0_amp.png}
		$8^{\mathrm{th}}$ H+V
		\includegraphics[width=1.0\linewidth]{2017injnocolc15o+19_6noerrut8skhv_dp0_amp_annotate.png}
	\caption{\label{fig:8th2017fmaamp} FMA analysis in amplitude space without excitation (left) and for $8^{\mathrm{th}}$~turn pulsing (right) based on the 2017 injection optics with no machine errors and a tune of (62.27,60.295). The excitation is 96~nrad in both planes. The $16Q_y$ and \mbox{$8Q_x-4Q_y$} are both excited.}

For excitation amplitudes smaller than 96~nrad no visible effect is indeed observed. In the horizontal and vertical plane a small emittance growth due to the excitation is visible, but without any clear dependency on the amplitude nor plane. Adducting the FMA analysis in amplitude space shown in Fig.~\ref{fig:8th2017fmaamp}, the $8^{\mathrm{th}}$ turn pulsing drives the $16Q_y$ and \mbox{$8Q_x-4Q_y$} resonances and several even higher orders. These are in general very high order resonances whose effect is thus expected to be small.

The only small effect on the beam expected from simulations could then be also confirmed experimentally during the 2017 experiment. For this purpose the excitation amplitude was increased to 96~nrad, which is the maximum kick strength reachable with the transverse damper at injection without risking saturation. As depicted in Fig.~\ref{fig:8thexploss}, the loss rate increased slightly with the excitation amplitude for an excitation in H+V. For an excitation only in V or only in H, no statistically relevant increase was observed.
\begin{figure}[h]
	\centering
	\includegraphics[width=1.0\linewidth]{2017_scale_amp_8hv_lbllong.png}
	\caption{\label{fig:8thexploss} Comparison of scaling of loss rates with excitation amplitude for $8^{\mathrm{th}}$~turn pulsing in H+V measured during the 2017 experiment. The excitation amplitude error is 15\% indicated by the horizontal error bars.}
\end{figure}

In the horizontal plane, a change in beam distribution was measured with the BSRT profiles (Appendix~\ref{app:sec:8}, Fig.~\ref{fig:8thexpprof}) for an excitation only in H, explicitly an increase of the distribution at around $2.0~\sigma$ simultaneously with a depletion of the beam core. For an excitation in H+V the emittances of the references bunches were much smaller, around $1.8~\mu$m normalized emittance on average, than the ones of the excited bunches ranging from $2.3~\mu$m to $3.0~\mu$m as described in \cite{resexmd2017}. The references bunches thus experienced a stronger emittance growth due to intra-beam scattering than the excited bunches due to the excitation on top of their smaller emittance growth due to intra-beam scattering. Therefore no excitation amplitude dependent emittance growth was observed for an excitation in H+V albeit it was recorded for an excitation only in H. In the vertical plane, the beam distribution and thus emittance stayed unchanged. For an excitation only in V, no dependence on the excitation was measured.

@@

\section{Additional plots for $7^{\mathrm{th}}$~turn pulsing during 2017 experiments}
\label{app:sec:7}
\begin{figure}[h]
	\begin{minipage}[t]{1.0\linewidth}
	\centering
	\includegraphics[width=0.8\linewidth]{2017_scale_amp_7h_lblshort.png}
	\end{minipage}
	\begin{minipage}[t]{1.0\linewidth}
		\centering
		\includegraphics[width=0.8\linewidth]{2017_scale_amp_7v_lblshort.png}
	\end{minipage}
	\begin{minipage}[t]{1.0\linewidth}
		\centering
		\includegraphics[width=0.8\linewidth]{2017_scale_amp_7hv_lblshort.png}
	\end{minipage}
	\caption{\label{fig:7thexploss2017} Comparison of scaling of loss rates with excitation amplitude for $7^{\mathrm{th}}$~turn pulsing only in H (top), only in V (center) and in H+V (bottom) during the 2017 experiment. The excitation amplitude error is 15\% indicated by horizontal error bars. The vertical errorbars represent the pure statistical error based on the averaging over several bunches with the same excitation amplitude.}
\end{figure}
\begin{figure}[h]
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		reference bunch,\\ no excitation
		\includegraphics[width=1.0\linewidth]{profile_v_7thhv_slot_2862.png}
	\end{minipage}
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		excited bunch,\\ $7^{\mathrm{th}}$~turn H+V	
		\includegraphics[width=1.0\linewidth]{profile_v_7thhv_slot_2696.png}
	\end{minipage}
	\caption{\label{fig:7thexpprof} Vertical beam profiles measured with the Beam Synchrotron Radiation Telescope (BSRT) during the 2017 experiments. The profiles are taken at the end of the $7^{\mathrm{th}}$~turn pulsing in H+V. For both bunches the transverse damper is not active. The distribution changes in the reference bunch (left), here slot 2862, are much less than for the bunch experiencing the maximum excitation (right), here slot 2696.}
\end{figure}

@@

\section{Additional plots for $8^{\mathrm{th}}$~turn pulsing during 2017 experiments}
\label{app:sec:8}
\begin{figure}[h]
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		reference bunch,\\ no excitation
		\includegraphics[width=1.0\linewidth]{profile_h_8thh_slot_804.png}
	\end{minipage}
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		excited bunch,\\ $8^{\mathrm{th}}$~turn H
		\includegraphics[width=1.0\linewidth]{profile_h_8thh_slot_632.png}
	\end{minipage}
	\caption{\label{fig:8thexpprof} Horizontal beam profiles measured with the Beam Synchrotron Radiation Telescope (BSRT) during the 2017 experiments. The profiles are taken at the end of the $8^{\mathrm{th}}$~turn pulsing in H. For both bunches the transverse damper is not active. The distribution changes in the reference bunch (left), here slot 804, are much less than for the bunch experiencing the maximum excitation (right), here slot 632.}
\end{figure}

>>>>

\section{Experimental and simulation setup\label{sec:exp}}
%put picture on top
\begin{figure*}
	\begin{minipage}[t]{1.0\linewidth}
		\centering
		2016 experiment\\
		\includegraphics[width=0.9\linewidth]{bunchfilling_2016.png}	
	\end{minipage}
	\begin{minipage}[t]{1.0\linewidth}
		\centering
		$ $\\
		2017 experiment\\
		\includegraphics[width=0.9\linewidth]{bunchfilling_2017.png}	
	\end{minipage}
	\caption{\label{fig:fill} Filling and excitation scheme for LHC experiments in 2016 (top) and 2017 (bottom). In 2016 a total of 48~bunches was used and in 2017 a total of 216~bunches. Each bunch is indicated with a cyan vertical bar. The bunches were grouped in sub-groups of 4~for 2016 and 6~for 2017 bunches, where each sub-group experienced the same excitation pattern and amplitude. The excitation amplitude is shown in blue and red. In 2016 the excitation was only applied in one plane. In 2017 more bunches could be injected without compromising machine protection making it possible to test all three planes in one fill.}
\end{figure*}
%put picture on top

@@

The ADT kicker deflection angle is calculated from the kicker geometry and the excitation voltage on the deflection plates. The excitation voltage used in the experiments is a complicated waveform, generated by a very complex hardware (digital signal processor, chain of transmission lines, low and high power amplifiers). The peak excitation voltage (and subsequently the kick) seen by the beam can be only indirectly measured using the probes on each kicker. The measured values are therefore believed to be known with an error margin of 10-15\% for the experiments in 2017 and 50\% in 2016. The estimate for 2017 is based on only a single measurement and in the future and with more time available the determination of the error would definitely have to be improved. The error in 2016 is an educated guess as no calibration was performed beforehand. The maximum kick strength reachable with the ADT at injection without risking saturation is 96~nrad. As an example Fig.~\ref{fig:fill_meas} shows the oscillation amplitude of each bunch in both H and V planes captured by the LHC real time transverse activity monitor during the 2017 experiments and an excitation with $8^{\mathrm{th}}$ turn pulsing. The measured activity is well in line with the expected excitation pattern.
\begin{figure}[h]
	\centering
	\includegraphics[width=1.0\linewidth]{bunchfilling_measured.png}	
	\caption{\label{fig:fill_meas} Bunch by bunch excitation detected by the real time transverse activity monitor during the 2017 experiment and an excitation with 8th turn pulsing.}
\end{figure}

@@

The losses measured during the experiment however differ from the simulations in terms of for which case the largest rate is observed as well as quantitatively for the specific cases. For example smaller losses are expected for the 2016 experiments compared to the 2017 experiments from simulations, while experimentally higher loss rates were measured in 2016 (see Fig.~\ref{fig:7thexploss}). For the 2017 experiment, the highest loss rates are expected for pulsing in H+V, than in H and then with a considerably reduction in V. During the experiment comparable loss rates are however measured for all three planes (see Appendix~\ref{app:sec:7}, Fig.~\ref{fig:7thexploss2017}). Last but not least the loss rates as defined in Eqn.~\ref{eqn:lossrate} for the 2016 (red and yellow) and 2017 (black and gree) experiments are compared in Fig.~\ref{fig:7thexploss}. In both cases and as also observed for the $10^{\mathrm{th}}$~turn pulsing, the loss rate follows a quadratic scaling with the excitation amplitude. Loss rates were in general higher during the 2016 experiments. The loss rates from simulations are not shown in Fig.~\ref{fig:7thexploss} as losses were only observed for much higher excitation amplitudes than tried in the experiments.
\begin{figure}[h]
	\centering
	\includegraphics[width=1.0\linewidth]{2016+2017_scale_amp_7h_lblshort.png}
	\caption{\label{fig:7thexploss} Comparison of scaling of loss rates with excitation amplitude for $7^{\mathrm{th}}$~turn pulsing in H and data obtained during the 2016 experiment (black and blue) and 2017 experiment (red and yellow). The excitation amplitude error is 50\% in 2016 and was reduced to 15\% in 2017. The solid and dashed line indicate the second order polynomial fit to the loss rate.}
\end{figure}

@@

\subsection{$8^{\mathrm{th}}$ turn pulsing\label{sec:simex8}}
Pulsing patterns which have little effect on the beam core are particularly interesting for the hollow electron lens operation if they in addition have a large effect on the halo. This is in general feasible considering the highly nonlinear field generated at the location of the halo particles by the HEL compared to no field or only a very small field at the location of the beam core. With this motivation in mind the $8^{\mathrm{th}}$~turn pulsing pattern was studied, for which a small effect in comparison to the $7^{\mathrm{th}}$ and $10^{\mathrm{th}}$ turn pulsing is expected (see Fig.~\ref{fig:8thsim}).
\begin{figure*}[h]
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		\includegraphics[width=1.0\linewidth]{2017injerra2b2uran1_2e-3_8th_3_5um_intensity.png}
	\end{minipage}
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		\includegraphics[width=1.0\linewidth]{2017injerra2b2uran1_2e-3_8th_3_5um_sigm.png}
	\end{minipage}
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		\includegraphics[width=1.0\linewidth]{2017injerra2b2uran1_2e-3_8th_3_5um_emit1.png}
	\end{minipage}	
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		\includegraphics[width=1.0\linewidth]{2017injerra2b2uran1_2e-3_8th_3_5um_emit2.png}
	\end{minipage}	
	\caption{\label{fig:8thsim} Relative intensity (top left), bunch length (top right), and horizontal (bottom left) and vertical (bottom right) emittance obtained from simulations (distribution tracking) based on the 2017 injection optics with standard errors and $(Q_x,Q_y)=(62.27,60.295)$. The solid line indicates an excitation with only a random dipole noise component in H+V of 6~nrad, and the dotted and dashed line the results for $8^{\mathrm{th}}$~turn pulsing plus a random dipole noise component in H+V of 6~nrad.}
\end{figure*}
\begin{figure}[t]
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		no excitation
		\includegraphics[width=1.0\linewidth]{2017injnocolc15o+19_6noerru_dp0_amp.png}
	\end{minipage}
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		$8^{\mathrm{th}}$ H+V
		\includegraphics[width=1.0\linewidth]{2017injnocolc15o+19_6noerrut8skhv_dp0_amp_annotate.png}
	\end{minipage}	
	\caption{\label{fig:8th2017fmaamp} FMA analysis in amplitude space without excitation (left) and for $8^{\mathrm{th}}$~turn pulsing (right) based on the 2017 injection optics with no machine errors and a tune of (62.27,60.295). The excitation is 96~nrad in both planes. The $16Q_y$ and \mbox{$8Q_x-4Q_y$} are both excited.}
\end{figure}
In simulations no visible effect is indeed observed for excitation amplitudes smaller than 96~nrad. In the horizontal and vertical plane a small emittance growth due to the excitation is visible, but without any clear dependence on the amplitude or plane. The FMA analysis in amplitude space reveals also the driven resonances (Fig.~\ref{fig:8th2017fmaamp}), which are the $16Q_y$ and \mbox{$8Q_x-4Q_y$} resonances and several even higher orders. These are in general very high order resonances whose effect is thus expected to be small.

\begin{figure}[h]
	\centering
	\includegraphics[width=1.0\linewidth]{2017_scale_amp_8hv_lblshort.png}
	\caption{\label{fig:8thexploss} Comparison of scaling of loss rates with excitation amplitude for $8^{\mathrm{th}}$~turn pulsing in H+V measured during the 2017 experiment. The excitation amplitude error is 15\% indicated by the horizontal error bars, the error on the loss rate is the error on the mean obtained through the average over the 6~bunches with the same excitation amplitude.}
\end{figure}
The small effect on the beam expected from simulations could then be also confirmed experimentally during the 2017 experiment. For this purpose the excitation amplitude was increased to the maximum reachable amplitude of 96~nrad. As depicted in Fig.~\ref{fig:8thexploss}, the loss rate increased slightly with the excitation amplitude for an excitation in H+V. For an excitation only in V or only in H, no statistically relevant increase was observed (see Appendix~\ref{app:sec:8}, Fig.~\ref{fig:8thexploss2017}). In the horizontal plane, a change in beam distribution was measured with the BSRT profiles (Appendix~\ref{app:sec:8}, Fig.~\ref{fig:8thexpprof}) for an excitation only in~H. The distribution increased around $2.0~\sigma$ simultaneously with a depletion of the beam core. For an excitation in H+V one would expect to see a similar distribution change. However, this change is not visible as the emittance of the references bunches was much smaller, around $1.8~\mu$m normalized emittance, compared to around $2.6~\mu$m for the excited bunches \cite{resexmd2017}. This difference in emittance then resulted in a stronger emittance growth due to intra-beam scattering for the reference bunches in comparison to the excited bunches making the additional emittance growth and distribution changes due to the excitation undetectable. In the vertical plane, the beam distribution and emittance were not affected by the resonant excitation.

@@

\section{Additional plots for $7^{\mathrm{th}}$~turn pulsing during 2017 experiments}
\label{app:sec:7}
\begin{figure}[h]
	\begin{minipage}[t]{1.0\linewidth}
	\centering
	\includegraphics[width=0.9\linewidth]{2017_scale_amp_7h_lblshort.png}
	\end{minipage}
	\begin{minipage}[t]{1.0\linewidth}
		\centering
		\includegraphics[width=0.9\linewidth]{2017_scale_amp_7v_lblshort.png}
	\end{minipage}
	\begin{minipage}[t]{1.0\linewidth}
		\centering
		\includegraphics[width=0.9\linewidth]{2017_scale_amp_7hv_lblshort.png}
	\end{minipage}
	\caption{\label{fig:7thexploss2017} Comparison of scaling of loss rates with excitation amplitude for $7^{\mathrm{th}}$~turn pulsing only in H (top), only in V (center) and in H+V (bottom) during the 2017 experiment. The excitation amplitude error is 15\% indicated by horizontal error bars. The vertical errorbars represent the pure statistical error based on the averaging over several bunches with the same excitation amplitude.}
\end{figure}
\begin{figure}[h]
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		reference bunch,\\ no excitation
		\includegraphics[width=1.0\linewidth]{profile_v_7thhv_slot_2862.png}
	\end{minipage}
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		excited bunch,\\ $7^{\mathrm{th}}$~turn H+V	
		\includegraphics[width=1.0\linewidth]{profile_v_7thhv_slot_2696.png}
	\end{minipage}
	\caption{\label{fig:7thexpprof} Vertical beam profiles measured with the Beam Synchrotron Radiation Telescope (BSRT) during the 2017 experiments. The profiles are taken at the end of the $7^{\mathrm{th}}$~turn pulsing in H+V. For both bunches the transverse damper is not active. The distribution changes in the reference bunch (left), here slot 2862, are much less than for the bunch experiencing the maximum excitation (right), here slot 2696.}
\end{figure}

@@

\section{Additional plots for $8^{\mathrm{th}}$~turn pulsing during 2017 experiments}
\label{app:sec:8}
\begin{figure}[h]
	\begin{minipage}[t]{1.0\linewidth}
		\centering
		\includegraphics[width=0.9\linewidth]{2017_scale_amp_8h_lblshort.png}
	\end{minipage}
	\begin{minipage}[t]{1.0\linewidth}
		\centering
		\includegraphics[width=0.9\linewidth]{2017_scale_amp_8v_lblshort.png}
	\end{minipage}
	\begin{minipage}[t]{1.0\linewidth}
		\centering
		\includegraphics[width=0.9\linewidth]{2017_scale_amp_8hv_lblshort.png}
	\end{minipage}
	\caption{\label{fig:8thexploss2017} Comparison of scaling of loss rates with excitation amplitude for $8^{\mathrm{th}}$~turn pulsing only in H (top), only in V (center) and in H+V (bottom) during the 2017 experiment. The excitation amplitude error is 15\% indicated by horizontal error bars. The vertical errorbars represent the pure statistical error based on the averaging over several bunches with the same excitation amplitude.}
\end{figure}
\begin{figure}[h]
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		reference bunch,\\ no excitation
		\includegraphics[width=1.0\linewidth]{profile_h_8thh_slot_804.png}
	\end{minipage}
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		excited bunch,\\ $8^{\mathrm{th}}$~turn H
		\includegraphics[width=1.0\linewidth]{profile_h_8thh_slot_632.png}
	\end{minipage}
	\caption{\label{fig:8thexpprof} Horizontal beam profiles measured with the Beam Synchrotron Radiation Telescope (BSRT) during the 2017 experiments. The profiles are taken at the end of the $8^{\mathrm{th}}$~turn pulsing in H. For both bunches the transverse damper is not active. The distribution changes in the reference bunch (left), here slot 804, are much less than for the bunch experiencing the maximum excitation (right), here slot 632.}
\end{figure}
